%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Development Engineer - Test} % Job title
    {Amazon - Device Advertising Products} % Organization
    {Seattle, WA} % Location
    {Aug. 2013 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Increased team productivity by 15\% through the creation of a unique Android application that could execute complex tasks at a push of a button, allowing internal Kindle Advertising teams to devote energy to other tasks.}
        \item {Decreased the estimated release schedule for new Over-The-Air updates for our application from 1 week down to 3 days by automating performance verification across all Kindle LCD device types, freeing up QA resources for other tasks and increasing confidence in our product.}
	\item {Developed a framework that would run automated integration tests on application builds after every new code push, allowing developers to catch bugs as soon as they are introduced, well before they ever reach customer devices.}
        \item {Coordinated with a small team of engineers to develop an automation framework for executing test cases on various devices, from FireTV to Kindle tablets running different operating systems.}
        \item {Developed and maintained automated test suites in a continuous deployment pipeline for our backend services that create and send ads to millions of devices each day.}
        \item {Drove several high-profile metrics processing issues to a close by constructing SQL queries to analyze production data in a unique way.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Rockwell Collins} % Organization
    {Cedar Rapids, IA} % Location
    {May 2011 - Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinated with a team of engineers to implement feature requests in a C / C++ based software application; a graphics engine running on aircraft cockpit displays.}
        \item {Developed a schema verification tool in python that could automatically identify a wide variety of issues in client applications, in some cases reducing our debugging time from hours down to minutes.}
        \item {Coordinated with teams in India and France to develop new graphical elements in our engine and debug issues in their development environments.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
